cardinalR: Generating interesting high-dimensional data structures

### 2025-06-24 paper-cardinalR.Rmd
Added overall paragraph for polynomial

>>>>

A polynomial structure generates data points that follow non-linear curvilinear relationships, such as quadratic or cubic trends, in high-dimensional space. These patterns are useful for evaluating how well algorithms capture smooth, non-linear trajectories and curvature in the data. We provide functions for generating quadratic and cubic structures, enabling controlled experiments with different degrees of polynomial complexity. Table `r knitr::asis_output(ifelse(knitr::is_html_output(), '\\@ref(tab:polynomial-tb-html)', '\\@ref(tab:polynomial-tb-pdf)'))` summarizes these functions and their purposes.

### 2025-06-24 paper-cardinalR.tex
Added overall paragraph for polynomial

>>>>

A polynomial structure generates data points that follow non-linear curvilinear relationships, such as quadratic or cubic trends, in high-dimensional space. These patterns are useful for evaluating how well algorithms capture smooth, non-linear trajectories and curvature in the data. We provide functions for generating quadratic and cubic structures, enabling controlled experiments with different degrees of polynomial complexity. Table \ref{tab:polynomial-tb-pdf} summarizes these functions and their purposes.
